Topic Modeling of News

### 2018-02-13 paper/R/02_cleanAndCombine.Rmd
ownership to site

### without stemming
processed <- textProcessor(btw$text_cleaned1, metadata = btw[,c("ownership","text_cleaned1","month")],
                           wordLengths = c(2,Inf),
                           lowercase = F,
                           removestopwords = F,
                           removenumbers = F,
                           removepunctuation = F,
                           stem = F)
out <- prepDocuments(processed$documents, processed$vocab, processed$meta)
out$meta$ownership <- as.factor(out$meta$ownership)
###

# processed <- textProcessor(btw$text_cleaned1, metadata = btw[,c("site","text_cleaned1","month")],
#                            wordLengths = c(2,Inf),
#                            lowercase = F,
#                            removestopwords = F,
#                            removenumbers = F,
#                            removepunctuation = F,
#                            stem = F)
# out <- prepDocuments(processed$documents, processed$vocab, processed$meta)
# out$meta$site <- as.factor(out$meta$site)

save(btw, out, file="../output/btw_comb.Rda")
```

>>>>

### without stemming
processed <- textProcessor(btw$text_cleaned1, metadata = btw[,c("site","text_cleaned1","month")],
                           wordLengths = c(2,Inf),
                           lowercase = F,
                           removestopwords = F,
                           removenumbers = F,
                           removepunctuation = F,
                           stem = F)
out <- prepDocuments(processed$documents, processed$vocab, processed$meta)
out$meta$site <- as.factor(out$meta$site)

save(btw, out, file="../output/btw_out.Rda")
```
